---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}

```

## How likely are dogs to eat in the first 24 hours after arriving at a Quarantine Facilty?
Imagine being put in a box, and then on a plane, for an undetermined amount of time and then suddenly you are in a new place with strange people. Would you still have an appetite?

This data is looking at whether or not a dog eats within 24 hours of arrival, and what sort of food is being offered. 



```{r}

library(tidyverse)
csv_file <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vSwN858bjItpjMDMXxz5a9t-uOpOHU4ntogGY6x054Il3A14FySzydRngWBNUF3MsRNIw3oP-m2Mb0t/pub?gid=431291523&single=true&output=csv"

# Rename data variables
logged_data <- read_csv(csv_file) %>%
rename( dog_weight = 2,
       dog_eaten = 3,
       food_provided = 4,
       health_issues = 5)

latest_data <- logged_data

paste0( "The weight of the smallest dog in this data is ", 
      min(logged_data$dog_weight), 
      "kg.", 
      collapse = " ")
paste0("The weight of the largest dog in this data is ", 
      max(logged_data$dog_weight), 
      "kg.",
      collapse = " ")

#Graph that shows what number of dogs have eaten within the first 24 hours of arrival.

ggplot(data = latest_data) +
  geom_bar(aes(x = dog_eaten),
           fill = "#28B85B") +
  labs(title = "Did the dog eat within 24 hours of arrival?",
       x = "Has the dog eaten",
       y = "Number of dogs")

# A graph that shows the type of food that has been provided to the dog. 

ggplot(data = latest_data) +
  geom_bar(aes(x = food_provided),
           fill = "#EB4646") +
  labs(title = "Food provided to dogs at Quarantine Facility",
       x = "Brand of dog food",
       y = "Number of dogs")

```

